---
title: "Robustness Check Plots"
output: html_document
---

1. import modeling results for each onset type
2. create robustness check plots

## read data

```{r}

library(ggplot2)
library(tidyverse)
library(broom)
library(dplyr)
library(sf)
library(sp)
library(tmap)
library(viridis)
library(leaflet)


#E:/R-code/Modeling/code/FCN_clean_csvs.R
#~/Documents/R-code

MT_outline <- readOGR(dsn = 'E:/R-code2/Modeling/data/shp/MatoGrossoOutline', layer = 'MatoGrossoOutline')
crs(MT_outline) <- CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

grid_1deg <- readOGR(dsn = 'E:/R-code2/Modeling/data/shp/grid_1deg', layer = 'grid_1deg')
munis <- readOGR(dsn = 'E:/R-code2/Modeling/data/shp/munis', layer = 'munis_SHP')
crs(munis) <- CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

# read in all the onsets. only the csv, not shp
all_onset_types <- c('Gabriel_onset', 'AA_2_persiann', 'AA_3_persiann', 
                      'AA_25_persiann', 'AA_25_chirps_ATgabriel25km', 'AA_25_persiann_ATgabriel25km',
                     'freq_5_persiann', 'freq_8_persiann', 'freq_10_persiann', 'freq_12_persiann',
                     'monsoon_30_persiann', 'monsoon_40_persiann',
                     'pentad_8_persiann', 'pentad_10_persiann', 'pentad_15_persiann',
                     'rangethres_10_15_15_30_persiann', 'rangethres_10_15_15_40_persiann',
                     'rangethres_10_15_20_20_persiann', 'rangethres_10_15_20_30_persiann',
                     'rangethres_10_15_30_40_persiann', 'thres_10_persiann',
                     'AA_25_chirps_ATchirps5km', 
                     'freq_5_chirps_ATchirps5km', 'freq_8_chirps_ATchirps5km', 
                     'freq_10_chirps_ATchirps5km', 'freq_12_chirps_ATchirps5km',
                     'rangethres_10_15_15_30_chirps_ATchirps5km',
                     'rangethres_10_15_15_40_chirps_ATchirps5km',
                     'rangethres_10_15_20_20_chirps_ATchirps5km',
                     'rangethres_10_15_20_30_chirps_ATchirps5km',
                     'rangethres_10_15_30_40_chirps_ATchirps5km')

```

## loop through each onset_type and generate cohesive data frame for all onset types

```{r}

# empty data frame to store results
all_results <- data.frame()

# add in results for each onset_type
for (onset_type in all_onset_types) {
  
  # read the data ---------------------------------------------------------------------------------------------------------
  filename <- paste0("E:/R-code2/Modeling/output/robustness_test/", onset_type, ".RData")
  loaded_data <- load(filename)
  
  #result_name <- paste0(onset_type, '_results')
  #assign(result_name, get(loaded_data))

  all_results <- rbind(all_results, get(loaded_data))
  
  rm(loaded_data) # Remove the old object since you've stored it in result_name

}
```


# what's the best onset definition for all grid offsets, for each crop intensity, plant stat intensity and model specification?
## model diagnostics: spatial autocorrelation

```{r} 

# model specifications to loop through.
# OLS_all_preds = onset, lat, lon, region, year_index
# OLS_space_only = onset, lat, lon, region
# OLS_year_only = onset, year_index
# OLS_no_preds = onset
model_specifications <- c("FE", "OLS_all_preds", "OLS_space_only", "OLS_year_only", "OLS_no_preds")

# save top five model specs in each model_spec x intensity x plant_stat_type
top_onsets <- data.frame()

for (model_specification in model_specifications) {

  for (crop_intensity in c("SC", "DC")) {
    for (plant_stat_type in c("median", "percentile25", "percentile5")) {
      
      if (model_specification == "FE") {
        results <- all_results[all_results$model_type == "FE" & 
                                 all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
      }
      
      if (model_specification == "OLS_all_preds") {
        results <- all_results[all_results$model_type == "OLS" & 
                                 all_results$lat_predictor == "yes" &
                                 all_results$year_predictor == "yes" &
                                 all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
      }
      
      if (model_specification == "OLS_space_only") {
        results <- all_results[all_results$model_type == "OLS" & 
                                 all_results$lat_predictor == "yes" &
                                 all_results$year_predictor == "no" &
                                 all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
      }
      
        if (model_specification == "OLS_year_only") {
          results <- all_results[all_results$model_type == "OLS" & 
                                   all_results$lat_predictor == "no" &
                                   all_results$year_predictor == "yes" &
                                   all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
        }
      
        if (model_specification == "OLS_no_preds") {
          results <- all_results[all_results$model_type == "OLS" & 
                                   all_results$lat_predictor == "no" &
                                   all_results$year_predictor == "no" &
                                   all_results$intensity == crop_intensity & 
                                   all_results$plant_stat_type == plant_stat_type,]
        }
      
      
      results$residual_autocorrelated <- results$moran_i_pval_residual <= 0.05
      
      # group by onset_type and calculate mean, median, min, max and stdev for each onset_type
      results_summary <- results %>% group_by(onset_type) %>%
                                    summarize(mean_onset_coef = mean(onset_coef),
                                              mean_onset_coef_stderr = mean(onset_coef_stderr),
                                              mean_year_coef = mean(year_coef),
                                              mean_year_coef_stderr = mean(year_coef_stderr),
                                              mean_R2 = mean(R2),
                                              mean_bias_meas = mean(bias_meas),
                                              mean_slope_onset_residual = mean(slope_onset_residual),
                                              mean_slope_fittedPlant_residual = mean(slope_fittedPlant_residual),
                                              mean_moran_i_residual = mean(moran_i_residual),
                                              mean_moran_i_pval_residual = mean(moran_i_pval_residual),
                                              
                                              sd_onset_coef = sd(onset_coef),
                                              sd_onset_coef_stderr = sd(onset_coef_stderr),
                                              sd_year_coef = sd(year_coef),
                                              sd_year_coef_stderr = sd(year_coef_stderr),
                                              sd_R2 = sd(R2),
                                              sd_bias_meas = sd(bias_meas),
                                              sd_slope_onset_residual = sd(slope_onset_residual),
                                              sd_slope_fittedPlant_residual = sd(slope_fittedPlant_residual),
                                              sd_moran_i_residual = sd(moran_i_residual),
                                              sd_moran_i_pval_residual = sd(moran_i_pval_residual),
                                              
                                              min_onset_coef = min(onset_coef),
                                              min_onset_coef_stderr = min(onset_coef_stderr),
                                              max_onset_coef = max(onset_coef),
                                              max_onset_coef_stderr = max(onset_coef_stderr),
                                              min_moran_i_pval_residual = min(moran_i_pval_residual),
                                              max_moran_i_pval_residual = max(moran_i_pval_residual),
                                              
                                              num_resid_autocorrelated = sum(residual_autocorrelated)
                                              )
      
      results_summary <- results_summary[order(results_summary$mean_onset_coef),]
      
      results_summary <- transform(results_summary, onset_type=reorder(onset_type, -mean_onset_coef) ) 
      
      # save top five onsets
      top_onsets <- rbind(top_onsets, data.frame(
                                                  model_specification = rep(model_specification, 5),
                                                  crop_intensity = rep(crop_intensity, 5),
                                                  plant_stat_type = rep(plant_stat_type, 5),
                                                  onset_type = results_summary$onset_type[(nrow(results_summary)-4):nrow(results_summary)]))
      
      best_onset_plot <- ggplot(results_summary) +
        geom_point(aes(x = onset_type, y = mean_onset_coef)) +
        geom_point(aes(x = onset_type,y = min_onset_coef), color = "blue") +
        geom_point(aes(x = onset_type, y = max_onset_coef), color = "red") +
        geom_errorbar(aes(x = onset_type, ymin= mean_onset_coef-sd_onset_coef, ymax=mean_onset_coef+sd_onset_coef)) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste(model_specification, ",", crop_intensity, ",", plant_stat_type)) +
        ylim(c(0, 0.6)) +
        ylab('onset coefficient')
      
      R2_plot <- ggplot(results_summary) +
        geom_point(aes(x = onset_type, y = mean_R2), color = "blue") +
        geom_errorbar(aes(x = onset_type, ymin= mean_R2-sd_R2, ymax=mean_R2+sd_R2)) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste(model_specification, ",", crop_intensity, ",", plant_stat_type)) +
        ylim(c(0, 0.7)) +
        ylab('R2')
      
      moran_i_pval_residual_plot <- ggplot(results_summary) +
        geom_point(aes(x = onset_type, y = mean_moran_i_pval_residual), color = "black") +
        geom_errorbar(aes(x = onset_type, ymin= mean_moran_i_pval_residual-sd_moran_i_pval_residual, 
                          ymax=mean_moran_i_pval_residual+sd_moran_i_pval_residual)) +
        geom_point(aes(x = onset_type,y = min_moran_i_pval_residual), color = "blue") +
        geom_point(aes(x = onset_type, y = max_moran_i_pval_residual), color = "red") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste(model_specification, ",", crop_intensity, ",", plant_stat_type)) +
        
        ylim(c(-0.2, 1.2)) +
        geom_hline(yintercept = 0.05, color = 'red') +
        ylab('p-val of morans I for residual')
      
      residual_autocorrelation_plot <- ggplot(results_summary) +
        geom_point(aes(x = onset_type, y = num_resid_autocorrelated), color = "black") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste(model_specification, ",", crop_intensity, ",", plant_stat_type)) +
        ylim(c(0, 14)) +
        ylab('number of times residual was autocorrelated')
      
      
      #print(best_onset_plot)
      print(R2_plot)
      #print(moran_i_pval_residual_plot)
      #print(residual_autocorrelation_plot)
      
      # percent residuals that are spatially autocorrelated
      # print(model_specification)
      # print(crop_intensity)
      # print(plant_stat_type)
      # print(paste('percent residuals that are spatially autocorrelated', 100*sum(results$moran_i_pval_residual <= 0.05)/nrow(results)))
    }
  }
}
```

## histograms of top onsets

```{r}

# only calc top onsets for FE
top_onsets_FE <- top_onsets[top_onsets$model_specification == "FE",]
top_onsets_FE_DC <- top_onsets_FE[top_onsets_FE$crop_intensity == "DC",]
top_onsets_FE_SC <- top_onsets_FE[top_onsets_FE$crop_intensity == "SC",]
top_onsets_FE_median <- top_onsets_FE[top_onsets_FE$plant_stat_type == "median",]
top_onsets_FE_percentile25 <- top_onsets_FE[top_onsets_FE$plant_stat_type == "percentile25",]
top_onsets_FE_percentile5 <- top_onsets_FE[top_onsets_FE$plant_stat_type == "percentile5",]

ggplot(top_onsets_FE, aes(x=reorder(onset_type, -table(onset_type)[onset_type]))) + geom_bar() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  ggtitle('Top onset definitions for FE; all crop intensities and plant stats') +
  xlab('onset type')

ggplot(top_onsets_FE_DC, aes(x=reorder(onset_type, -table(onset_type)[onset_type]))) + geom_bar() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  ggtitle('Top onset definitions for FE and DC; all plant stats') +
  xlab('onset type')

ggplot(top_onsets_FE_SC, aes(x=reorder(onset_type, -table(onset_type)[onset_type]))) + geom_bar() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  ggtitle('Top onset definitions for FE and SC; all plant stats') +
  xlab('onset type')

ggplot(top_onsets_FE_median, aes(x=reorder(onset_type, -table(onset_type)[onset_type]))) + geom_bar() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  ggtitle('Top onset definitions for FE and median; all crop intensities') +
  xlab('onset type')

ggplot(top_onsets_FE_percentile25, aes(x=reorder(onset_type, -table(onset_type)[onset_type]))) + geom_bar() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  ggtitle('Top onset definitions for FE and percentile25; all crop intensities') +
  xlab('onset type')

ggplot(top_onsets_FE_percentile5, aes(x=reorder(onset_type, -table(onset_type)[onset_type]))) + geom_bar() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  ggtitle('Top onset definitions for FE and percentile5; all crop intensities') +
  xlab('onset type')
```

## model diagnostics: R2

```{r}

  for (crop_intensity in c("SC", "DC")) {
    for (plant_stat_type in c("median", "percentile25", "percentile5")) {
      
        results_FE <- all_results[all_results$model_type == "FE" & 
                                 all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
        results_FE$model_spec = "FE"
      
        results_OLS <- all_results[all_results$model_type == "OLS" & 
                                 all_results$lat_predictor == "yes" &
                                 all_results$year_predictor == "yes" &
                                 all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
        results_OLS$model_spec = "OLS"
      
      
        results <- rbind(results_FE, results_OLS)
        
      # group by onset_type and calculate mean, median, min, max and stdev for each onset_type
      results_summary <- results %>% group_by(onset_type, model_spec) %>%
                                    summarize(mean_onset_coef = mean(onset_coef),
                                              mean_onset_coef_stderr = mean(onset_coef_stderr),
                                              mean_R2 = mean(R2),
                                              
                                              sd_onset_coef = sd(onset_coef),
                                              sd_onset_coef_stderr = sd(onset_coef_stderr),
                                              sd_R2 = sd(R2)
                                              )
      
      results_summary <- results_summary[order(results_summary$mean_onset_coef),]
      
      results_summary <- transform(results_summary, onset_type=reorder(onset_type, -mean_onset_coef) ) 
      
      R2_plot <- ggplot(results_summary) +
        geom_point(aes(x = onset_type, y = mean_R2, col = model_spec)) +
        geom_errorbar(aes(x = onset_type, ymin= mean_R2-sd_R2, ymax=mean_R2+sd_R2)) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste(model_specification, ",", crop_intensity, ",", plant_stat_type)) +
        ylim(c(0, 0.7)) +
        ylab('R2')
      
      print(R2_plot)
    }
  }


```

## sensitivity to type of onset definitions vs sensitivity to the specific thresholds chosen
## only look at FE and persiann

```{r}


onset_def_types <- c("AA", "freq", "monsoon", "pentad", "rangethres", "thres")

# save top five model specs in each model_spec x intensity x plant_stat_type
top_onsets <- data.frame()


  for (crop_intensity in c("SC", "DC")) {
    
    for (plant_stat_type in c("median", "percentile25", "percentile5")) {
      
      
        results <- all_results[all_results$model_type == "FE" & 
                                 all_results$precip_data == "persiann" &
                                 all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
      
      # group by onset_type and calculate mean, median, min, max and stdev for each onset_type
      results_summary <- results %>% group_by(onset_def_type) %>%
                                    summarize(mean_onset_coef = mean(onset_coef),
                                              mean_onset_coef_stderr = mean(onset_coef_stderr),
                                              mean_year_coef = mean(year_coef),
                                              mean_year_coef_stderr = mean(year_coef_stderr),
                                              mean_moran_i_pval_residual = mean(moran_i_pval_residual),
                                              mean_moran_i_pval_onset = mean(moran_i_pval_onset),
                                              
                                              sd_onset_coef = sd(onset_coef),
                                              sd_onset_coef_stderr = sd(onset_coef_stderr),
                                              sd_year_coef = sd(year_coef),
                                              sd_year_coef_stderr = sd(year_coef_stderr),
                                              sd_moran_i_pval_residual = sd(moran_i_pval_residual),
                                              sd_moran_i_pval_onset = sd(moran_i_pval_onset),

                                              min_onset_coef = min(onset_coef),
                                              min_onset_coef_stderr = min(onset_coef_stderr),
                                              max_onset_coef = max(onset_coef),
                                              max_onset_coef_stderr = max(onset_coef_stderr),
                                              min_moran_i_pval_residual = min(moran_i_pval_residual),
                                              min_moran_i_pval_onset = min(moran_i_pval_onset)
                                              )
      

      results_summary <- results_summary[order(results_summary$mean_onset_coef),]

      results_summary <- transform(results_summary, onset_def_type=reorder(onset_def_type, -mean_onset_coef) ) 

      best_onset_plot <- ggplot(results_summary) +
        geom_point(aes(x = onset_def_type, y = mean_onset_coef)) +
        geom_point(aes(x = onset_def_type,y = min_onset_coef), color = "blue") +
        geom_point(aes(x = onset_def_type, y = max_onset_coef), color = "red") +
        geom_errorbar(aes(x = onset_def_type, ymin= mean_onset_coef-sd_onset_coef, ymax=mean_onset_coef+sd_onset_coef)) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste("FE ,", crop_intensity, ",", plant_stat_type)) +
        ylim(c(0, 0.6)) +
        ylab('onset coefficient')

      moran_i_pval_residual_plot <- ggplot(results_summary) +
        geom_point(aes(x = onset_def_type, y = mean_moran_i_pval_residual), color = "black") +
        geom_errorbar(aes(x = onset_def_type, ymin= mean_moran_i_pval_residual-sd_moran_i_pval_residual, 
                          ymax=mean_moran_i_pval_residual+sd_moran_i_pval_residual)) +
        geom_point(aes(x = onset_def_type,y = min_moran_i_pval_residual), color = "blue") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste("FE ,", crop_intensity, ",", plant_stat_type)) +
        ylim(c(-0.2, 1.2)) +
        geom_hline(yintercept = 0.05, color = 'red') +
        ylab('p-val of morans I for residual')
      
      moran_i_pval_onset_plot <- ggplot(results_summary) +
        geom_point(aes(x = onset_def_type, y = mean_moran_i_pval_onset), color = "black") +
        geom_errorbar(aes(x = onset_def_type, ymin= mean_moran_i_pval_onset-sd_moran_i_pval_onset, 
                          ymax=mean_moran_i_pval_onset+sd_moran_i_pval_onset)) +
        geom_point(aes(x = onset_def_type,y = min_moran_i_pval_onset), color = "blue") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste("FE ,", crop_intensity, ",", plant_stat_type)) +
        ylim(c(-0.2, 1.2)) +
        geom_hline(yintercept = 0.05, color = 'red') +
        ylab('p-val of morans I for onset')
      
      #print(best_onset_plot)
      #print(moran_i_pval_residual_plot)
      print(moran_i_pval_onset_plot)
    }
  }


```



## Does onset coefficient change more across grid offsets and missing predictors than for different onset definitions, intensities, and plant stat types? (i.e. can we trust that the differences in onset coef that we WANT to see are larger than the 'noise'?)

```{r}

chosen_onset_types <- c("freq_10_persiann", "rangethres_10_15_15_40_persiann", "rangethres_10_15_30_40_persiann", "freq_12_persiann",
                        "freq_8_persiann", "rangethres_10_15_20_30_persiann")

for (onset_type in chosen_onset_types) {
      
      
        results_FE <- all_results[all_results$model_type == "FE" & 
                                 all_results$onset_type == onset_type,]
        results_FE$model_spec = "FE"
      
        results_OLSall <- all_results[all_results$model_type == "OLS" & 
                                 all_results$lat_predictor == "yes" &
                                 all_results$year_predictor == "yes" &
                                 all_results$onset_type == onset_type,]
        results_OLSall$model_spec = "OLS_all"
      
      
        results_OLSnone <- all_results[all_results$model_type == "OLS" & 
                                 all_results$lat_predictor == "no" &
                                 all_results$year_predictor == "no" &
                                 all_results$onset_type == onset_type,]
        results_OLSnone$model_spec = "OLS_none"
        
        results <- rbind(results_FE, results_OLSall, results_OLSnone)
        
        results <- unite(results, col = "desc", model_spec, intensity, plant_stat_type, remove = FALSE)
        
      # group by onset_type and calculate mean, median, min, max and stdev for each onset_type
      results_summary <- results %>% group_by(desc, model_spec, plant_stat_type, intensity) %>%
                                    summarize(mean_onset_coef = mean(onset_coef),
                                              mean_onset_coef_stderr = mean(onset_coef_stderr),
                                              mean_R2 = mean(R2),
                                              
                                              sd_onset_coef = sd(onset_coef),
                                              sd_onset_coef_stderr = sd(onset_coef_stderr),
                                              sd_R2 = sd(R2)
                                              )
      
      
      onset_coef_plot <- ggplot(results_summary) +
        geom_point(aes(x = desc, y = mean_onset_coef, col = model_spec, shape = intensity)) +
        geom_errorbar(aes(x = desc, ymin= mean_onset_coef-sd_onset_coef, ymax=mean_onset_coef+sd_onset_coef, col = model_spec)) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste(onset_type)) +
        ylim(c(0, 0.7)) +
        ylab('onset coef')
      
      print(onset_coef_plot)
    }
  

```

## look at onset coef's sensitivity to eliminated predictors in OLS

```{r}

onset_type <- "freq_10_persiann"
for (crop_intensity in c("SC", "DC")) {
    for (plant_stat_type in c("median", "percentile25", "percentile5")) {
      
        results_FE <- all_results[all_results$model_type == "FE" & 
                                 all_results$onset_type == onset_type &
                                  all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
        results_FE$model_spec = "FE"
     
        results_OLSall <- all_results[all_results$onset_type == onset_type &
                                 all_results$model_type == "OLS" & 
                                 all_results$lat_predictor == "yes" &
                                 all_results$year_predictor == "yes" &
                                 all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
      
        results_OLSspaceonly <- all_results[all_results$onset_type == onset_type &
                                 all_results$model_type == "OLS" & 
                                 all_results$lat_predictor == "yes" &
                                 all_results$year_predictor == "no" &
                                 all_results$intensity == crop_intensity & 
                                 all_results$plant_stat_type == plant_stat_type,]
      
        results_OLSyearonly <- all_results[all_results$onset_type == onset_type &
                                all_results$model_type == "OLS" & 
                                all_results$lat_predictor == "no" &
                                all_results$year_predictor == "yes" &
                                all_results$intensity == crop_intensity & 
                                all_results$plant_stat_type == plant_stat_type,]

        results_OLSnone <- all_results[all_results$onset_type == onset_type &
                                   all_results$model_type == "OLS" & 
                                   all_results$lat_predictor == "no" &
                                   all_results$year_predictor == "no" &
                                   all_results$intensity == crop_intensity & 
                                   all_results$plant_stat_type == plant_stat_type,]
      
        results_FE$model_spec = "FE"
        results_OLSall$model_spec = "OLS_all"
        results_OLSspaceonly$model_spec = "OLS_spaceonly"
        results_OLSyearonly$model_spec = "OLS_yearonly"
        results_OLSnone$model_spec = "OLS_none"
        
        results <- rbind(results_FE, results_OLSall, results_OLSspaceonly, results_OLSyearonly, results_OLSnone)
        results <- unite(results, col = "desc", model_spec, intensity, plant_stat_type, remove = FALSE)
        
        # group by onset_type and calculate mean, median, min, max and stdev for each onset_type
        results_summary <- results %>% group_by(model_spec) %>%
                                    summarize(mean_onset_coef = mean(onset_coef),
                                              mean_onset_coef_stderr = mean(onset_coef_stderr),
                                              
                                              
                                              sd_onset_coef = sd(onset_coef),
                                              sd_onset_coef_stderr = sd(onset_coef_stderr),
                                              
                                              
                                              min_onset_coef = min(onset_coef),
                                              min_onset_coef_stderr = min(onset_coef_stderr),
                                              max_onset_coef = max(onset_coef),
                                              max_onset_coef_stderr = max(onset_coef_stderr)
                                              )
      
      onset_coef_plot <- ggplot(results_summary) +
        geom_point(aes(x = model_spec, y = mean_onset_coef)) +
        geom_point(aes(x = model_spec,y = min_onset_coef), color = "blue") +
        geom_point(aes(x = model_spec, y = max_onset_coef), color = "red") +
        geom_errorbar(aes(x = model_spec, ymin= mean_onset_coef-sd_onset_coef, ymax=mean_onset_coef+sd_onset_coef)) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90)) +
        ggtitle(paste0(onset_type, ", ", crop_intensity, ", ", plant_stat_type)) +
        ylim(c(0, 0.6)) +
        ylab('onset coefficient')
      
      print(onset_coef_plot)
    }
  }

```