---
title: "Robustness Check"
output: html_document
---

1. run model for different grid offset, model specification, onset definitions
2. record model diagnostics and performance (onset coef, residuals, etc)
3. save model diagnostics as RData
4. plots

## read data

```{r}

library(ggplot2)
library(tidyverse)
library(broom)
library(dplyr)
library(rgdal)
library(rgeos)
library(raster)
library(sf)
library(sp)
library(tmap)
library(viridis)
library(spdep)
library(spatialreg)
library(lmtest)
library(Metrics) # for rmse
library(leaflet)

#E:/R-code/Modeling/code/FCN_clean_csvs.R
#~/Documents/R-code
source('E:/R-code2/Modeling/code/FCN_clean_csvs.R')
source('E:/R-code2/Modeling/code/FCN_plotting.R')
source('E:/R-code2/Modeling/code/FCN_sample_data.R')
source('E:/R-code2/Modeling/code/FCN_run_model_spatial_sampled.R')

onset_type <- 'AA_25_chirps_ATgabriel25km' #''AA_25_chirps_ATgabriel25km' # 'Gabriel_onset'
grid_size <- 0.75 # 0.5 for 5 km onset, 0.75 for 25 km onset
precip_data <- 'chirps'
onset_def_type <- 'AA'
thres <- '2.5' # keep as string; some will have two or four thres
onset_scale <- '25km_Gabriel' # 5km_chirps, 25km_Gabriel, 25km_persiann, 25km_chirps
year_oi <- 2014 # for spatial autocorrelation

if (onset_type != 'Gabriel_onset') {
  filename_median <- paste0('E:/R-code-large-files/data_onset_', onset_type, '/median_onset_cell_', onset_type, '.csv')
  filename_percentile5 <- paste0('E:/R-code-large-files/data_onset_', onset_type, '/percentile5_onset_cell_', onset_type, '.csv')
  filename_percentile25 <- paste0('E:/R-code-large-files/data_onset_', onset_type, '/percentile25_onset_cell_', onset_type, '.csv')

  filename_shp<- paste0('E:/R-code-large-files/data_onset_', onset_type, '/shp')
  layername_shp <- paste0('median_onset_cell_SHP_', onset_type)
  
  median_cell_raw <- read.csv(filename_median)
  percentile5_cell_raw <- read.csv(filename_percentile5)
  percentile25_cell_raw <- read.csv(filename_percentile25)
  
  cell_sf <- st_read(dsn = filename_shp, layer = layername_shp)
}

if (onset_type == 'Gabriel_onset') {
  median_cell_raw <- read.csv('E:/R-code2/Modeling/data/median_onset_cell_v3.csv')
  percentile5_cell_raw <- read.csv('E:/R-code2/Modeling/data/percentile5_onset_cell_v3.csv')
  percentile25_cell_raw <- read.csv('E:/R-code2/Modeling/data/percentile25_onset_cell_v3.csv')
  
  cell_sf <- st_read(dsn = 'E:/R-code2/Modeling/data/shp/median_onset_cell_v3', layer = 'median_onset_cell_SHP_v3')
}


MT_outline <- readOGR(dsn = 'E:/R-code2/Modeling/data/shp/MatoGrossoOutline', layer = 'MatoGrossoOutline')
crs(MT_outline) <- CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

grid_1deg <- readOGR(dsn = 'E:/R-code2/Modeling/data/shp/grid_1deg', layer = 'grid_1deg')
munis <- readOGR(dsn = 'E:/R-code2/Modeling/data/shp/munis', layer = 'munis_SHP')
crs(munis) <- CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

# read in all the onsets. only the csv, not shp
all_onset_types <- c('Gabriel_onset', 'AA_2_persiann', 'AA_3_persiann', 
                      'AA_25_persiann', 'AA_25_chirps_ATgabriel25km', 'AA_25_persiann_ATgabriel25km',
                     'freq_5_persiann', 'freq_8_persiann', 'freq_10_persiann', 'freq_12_persiann',
                     'monsoon_30_persiann', 'monsoon_40_persiann',
                     'pentad_8_persiann', 'pentad_10_persiann', 'pentad_15_persiann',
                     'rangethres_10_15_15_30_persiann', 'rangethres_10_15_15_40_persiann',
                     'rangethres_10_15_20_20_persiann', 'rangethres_10_15_20_30_persiann',
                     'rangethres_10_15_30_40_persiann', 'thres_10_persiann',
                     'AA_25_chirps_ATchirps5km', 
                     'freq_5_chirps_ATchirps5km', 'freq_8_chirps_ATchirps5km', 
                     'freq_10_chirps_ATchirps5km', 'freq_12_chirps_ATchirps5km',
                     'rangethres_10_15_15_30_chirps_ATchirps5km',
                     'rangethres_10_15_15_40_chirps_ATchirps5km',
                     'rangethres_10_15_20_20_chirps_ATchirps5km',
                     'rangethres_10_15_20_30_chirps_ATchirps5km',
                     'rangethres_10_15_30_40_chirps_ATchirps5km')
```

## read and clean spatial data

```{r}

# CSV DATA -----------------------------------------------------------------------------------------------------------------
# median cell
median_cell <- median_cell_raw %>% delete_cols_median_cell() %>%
                                    rename_cols_median_cell()
median_cell$plant_stat_type <- rep('median', nrow(median_cell))


# percentiles
percentile5_cell <- percentile5_cell_raw %>% rename_cols_percentile_cell()
percentile25_cell <- percentile25_cell_raw %>% rename_cols_percentile_cell()

# SF DATA ------------------------------------------------------------------------------------------------

# get cell_ID column for median
cell_sf$cell_ID <- median_cell$cell_ID
cell_sf$cell_ID <- sapply(as.character(cell_sf$cell_ID), clean_cell_ID)

# join median, percentile data to cell_sf
# cell_sf has median information, but copy it and put in percentile info for DC and SC plant

cell_sf$plant_stat_type <- rep("median", nrow(cell_sf))

cell_sf_percentile5 <- cell_sf
cell_sf_percentile5$SC_plant <- percentile5_cell$SC_plant
cell_sf_percentile5$DC_plant <- percentile5_cell$DC_plant
cell_sf_percentile5$plant_stat_type <- rep("percentile5", nrow(cell_sf_percentile5))

cell_sf_percentile25 <- cell_sf
cell_sf_percentile25$SC_plant <- percentile25_cell$SC_plant
cell_sf_percentile25$DC_plant <- percentile25_cell$DC_plant
cell_sf_percentile25$plant_stat_type <- rep("percentile25", nrow(cell_sf_percentile25))

cell_sf <- rbind(cell_sf, cell_sf_percentile5, cell_sf_percentile25)

cell_sf_tidy <- cell_sf %>% tidy_by_intensity_plant("SC_plant", "DC_plant") %>%
            #tidy_by_intensity_delay("SC_delay", "DC_delay") %>%
            dplyr::select(-c(SC_harvest, DC_harvest)) %>%
            categorize_regions_cell_sf_tidy() # categorize cells into four regions

cell_sf_tidy$year_index <- cell_sf_tidy$year - 2003
cell_sf_tidy$year_factor <- as.factor(cell_sf_tidy$year)

cell_sf_tidy <- cell_sf_tidy %>%  drop_na
cell_sf_tidy$delay <- cell_sf_tidy$plant - cell_sf_tidy$onset

# split into SC and DC cells
cell_sf_tidy_SC <- cell_sf_tidy[cell_sf_tidy$intensity == "SC",]
cell_sf_tidy_DC <- cell_sf_tidy[cell_sf_tidy$intensity == "DC",]

# plotting
year <- 2013
cell_year <- cell_sf_tidy[cell_sf_tidy$year == year, ]
  
onset_map <- ggplot(cell_year) +
  geom_sf(aes(fill = onset)) +
  scale_fill_viridis() +
  ggtitle(paste("Onset for spatial sampling", year, onset_type)) +
  geom_polygon(data = MT_outline, aes(x = long, y = lat), color = "black", alpha = 0, linetype = 1) +
  theme_bw()

#print(onset_map)
  
```

## define descriptors for the chosen onset definition

```{r}



# define model specification alternatives

lat_offsets <- seq(0, 0.75, by = 0.25) # seq(0,0.25, by = 0.25)
lon_offsets <- seq(0, 0.75, by = 0.25) # seq(0,0.25, by = 0.25)
crop_intensities <- c('SC', 'DC')
plant_stat_types <- c('median', 'percentile5', 'percentile25')

# the dataframe to add results to. output this at the end for each onset_type
output_results <- data.frame(

  model_type <- character(0), # FE or OLS
  intensity = character(0),
  plant_stat_type = character(0),
  lat_predictor = character(0), # to indicate the presence of predictors. yes or no. NA if using fixed effects
  lon_predictor = character(0),
  year_predictor = character(0),
  region_predictor = character(0),
  
  onset_type = character(0),
  precip_data = character(0),
  onset_def_type = character(0),
  thres = character(0),
  onset_scale = character(0),
  
  grid_size = numeric(0),
  grid_offset_lat = numeric(0),
  grid_offset_lon = numeric(0),
  
  onset_coef = numeric(0),
  onset_coef_stderr = numeric(0),
  year_coef = numeric(0),
  year_coef_stderr = numeric(0),
  lat_coef = numeric(0),
  lat_coef_stderr = numeric(0),
  
  R2 = numeric(0),
  bias_meas = numeric(0), # slope of predicted plant to residual
  slope_onset_residual = numeric(0),
  slope_fittedPlant_residual = numeric(0),
  
  moran_i_residual = numeric(0),
  moran_i_pval_residual = numeric(0),
  moran_i_onset = numeric(0),
  moran_i_pval_onset = numeric(0),
  moran_i_plant = numeric(0),
  moran_i_pval_plant = numeric(0)
)
```


## for the chosen onset type, loop through FE model specifications

```{r}

library(plm) # for FE

# FE model specifications
counter = 0

for (lat_offset in lat_offsets) {
  for (lon_offset in lon_offsets) {
    for (plant_stat_type in plant_stat_types) {
      for (crop_intensity in crop_intensities) {
  
        if (crop_intensity == 'SC') {cell_sf_tidy_intensity <- cell_sf_tidy_SC}
        if (crop_intensity == 'DC') {cell_sf_tidy_intensity <- cell_sf_tidy_DC}
        
        # sample from full data and turn into data frame
        sampled <- get_sampled_data(full_data = cell_sf_tidy_intensity, plant_stat = plant_stat_type, grid_size = grid_size,
                         lat_offset = lat_offset, lon_offset = lon_offset, agg_scheme = FALSE, plot_samples = FALSE, year_oi = year_oi)
        st_geometry(sampled) <- NULL
        
        
        # for plm, first set data as panel data
        panel <- pdata.frame(sampled,index = c("cell_ID"))
        
        # FE model
        fe_result <- plm(plant ~ onset + year_index, data = panel, model = "within")
        
        # save coefficients
        onset_coef <- summary(fe_result)$coefficients['onset',]['Estimate']
        onset_coef_stderr <- summary(fe_result)$coefficients['onset',]['Std. Error']
        year_coef <- summary(fe_result)$coefficients['year_index',]['Estimate']
        year_coef_stderr <- summary(fe_result)$coefficients['onset',]['Std. Error']
        
        # R2
        SST <- sum((sampled$plant - mean(sampled$plant))^2)
        SSE <- sum((fe_result$residuals - mean(fe_result$residuals))^2)
        R2 <- 1 - SSE/SST
        
        # model diagnostics: residual, observed plant and fitted plant
        error_df <- data.frame(residual = fe_result$residuals,
                               observed = sampled$plant,
                               fitted =  sampled$plant - fe_result$residuals,
                               onset = sampled$onset)
        
        bias_model <- lm(residual ~ observed, data = error_df)
        bias_measure <- bias_model$coefficients['observed']
        
        onset_residual_model <- lm(residual ~ onset, data = error_df)
        onset_residual_slope <- onset_residual_model$coefficients['onset']
        
        fitted_residual_model <- lm(residual ~ fitted, data = error_df)
        fitted_residual_slope <- fitted_residual_model$coefficients['fitted']
        
        # model diagnostics: spatial autocorrelation of residuals, onset, plant
        # sample again and keep geometry
        sampled_withGeom <- get_sampled_data(full_data = cell_sf_tidy_intensity, plant_stat = plant_stat_type, grid_size = grid_size,
                         lat_offset = lat_offset, lon_offset = lon_offset, agg_scheme = FALSE, plot_samples = FALSE, year_oi = year_oi)
        
        sampled_withGeom$residuals <- fe_result$residuals
        
        to_autocorrelation <- sampled_withGeom[sampled_withGeom$year == year_oi, ]
        to_autocorrelation_sp <- as(to_autocorrelation, "Spatial")
        st_geometry(to_autocorrelation) <- NULL # turn to_autocorrelation into data frame
        centroids <- coordinates(to_autocorrelation_sp)
        to_autocorrelation_points <- SpatialPointsDataFrame(coords = centroids, data = to_autocorrelation)
        nb<-knn2nb(knearneigh(to_autocorrelation_points)) 
        lw <- nb2listw(nb, zero.policy = TRUE)
        
        # calculate spatial autocorrelation
        moran_residual <- moran.mc(to_autocorrelation_points$residuals, lw, 500, zero.policy = TRUE)
        moran_onset <- moran.mc(to_autocorrelation_points$onset, lw, 500, zero.policy = TRUE)
        moran_plant <- moran.mc(to_autocorrelation_points$plant, lw, 500, zero.policy = TRUE)
        
        moran_i_residual <- moran_residual$statistic
        moran_i_pval_residual <- moran_residual$p.value
        moran_i_onset <- moran_onset$statistic
        moran_i_pval_onset <- moran_onset$p.value
        moran_i_plant <- moran_plant$statistic
        moran_i_pval_plant <- moran_plant$p.value
        
        # save
        output_row <- data.frame(
          
          model_type = 'FE',
          intensity = crop_intensity, plant_stat_type = plant_stat_type,
         
          lat_predictor = 'NA', lon_predictor = 'NA',
          year_predictor = 'yes', region_predictor = 'NA',
  
          onset_type = onset_type, precip_data = precip_data, onset_def_type = onset_def_type, 
          thres = thres, onset_scale = onset_scale,
          
          grid_size = grid_size, grid_offset_lat = lat_offset, grid_offset_lon = lon_offset,
          
          onset_coef = onset_coef, onset_coef_stderr = onset_coef_stderr,
          year_coef = year_coef, year_coef_stderr = year_coef_stderr,
          lat_coef = NA, lat_coef_stderr = NA,
          
          
          R2 = R2, bias_meas = bias_measure, # slope of predicted plant to residual
          slope_onset_residual = onset_residual_slope, slope_fittedPlant_residual = fitted_residual_slope,
          
          moran_i_residual = moran_i_residual, moran_i_pval_residual = moran_i_pval_residual,
          moran_i_onset = moran_i_onset, moran_i_pval_onset = moran_i_pval_onset,
          moran_i_plant = moran_i_plant, moran_i_pval_plant = moran_i_pval_plant
        )
        
        output_results <- rbind(output_results, output_row)
        
        counter = counter + 1
        print(counter)
      }
    }
  }
}

# export test results
filename = paste0('E:/R-code2/Modeling/output/robustness_test/', onset_type, '_FE.RData')
save(output_results, file = filename)
```

## for the chosen onset type, loop through OLS model specifications

```{r}

# list of predictor sets to use
predictors_list <- list(
  c("onset", "region", "lat", "lon", "year_index"),
  c("onset", "region", "lat", "lon"),
  c("onset", "year_index"),
  c("onset")
  )

counter = 0

for (lat_offset in lat_offsets) {
  for (lon_offset in lon_offsets) {
    for (plant_stat_type in plant_stat_types) {
      for (crop_intensity in crop_intensities) {
        for (predictors in predictors_list) {
  
          if (crop_intensity == 'SC') {cell_sf_tidy_intensity <- cell_sf_tidy_SC}
          if (crop_intensity == 'DC') {cell_sf_tidy_intensity <- cell_sf_tidy_DC}
          
          # sample from full data and turn into data frame
          sampled <- get_sampled_data(full_data = cell_sf_tidy_intensity, plant_stat = plant_stat_type, grid_size = grid_size,
                           lat_offset = lat_offset, lon_offset = lon_offset, agg_scheme = FALSE, plot_samples = FALSE, year_oi = year_oi)
          
          
          # OLS
          # define the formula
          formula.string <- paste("plant", paste(predictors, collapse = " + "), sep = " ~ ")
          f <- as.formula(formula.string)
    
          # do the model
    
          ols_model = lm(f, data=sampled) 
          sampled$residuals <- residuals(ols_model)
          sampled$fitted.values <- fitted.values(ols_model)
          
          # save coefficients
          coefficients <- ols_model$coefficients
          onset_coef <- coefficients["onset"]
          year_coef <- coefficients["year_index"]
          lat_coef <- coefficients["lat"]
          
          std_errors <- summary(ols_model)$coefficients[,2]
          onset_coef_stderr <- std_errors["onset"]
          year_coef_stderr <- std_errors["year_index"]
          lat_coef_stderr <- std_errors["lat"]
  
          # R2
          SST <- sum((sampled$plant - mean(sampled$plant))^2)
          SSE <- sum((sampled$residuals - mean(sampled$residuals))^2)
          R2 <- 1 - SSE/SST
          
          # model diagnostics: residual, observed plant and fitted plant
          error_df <- data.frame(residual = sampled$residuals,
                                 observed = sampled$plant,
                                 fitted =  sampled$fitted.values,
                                 onset = sampled$onset)
          
          bias_model <- lm(residual ~ observed, data = error_df)
          bias_measure <- bias_model$coefficients['observed']
          
          onset_residual_model <- lm(residual ~ onset, data = error_df)
          onset_residual_slope <- onset_residual_model$coefficients['onset']
          
          fitted_residual_model <- lm(residual ~ fitted, data = error_df)
          fitted_residual_slope <- fitted_residual_model$coefficients['fitted']
          
          # model diagnostics: spatial autocorrelation of residuals, onset, plant
          to_autocorrelation <- sampled[sampled$year == year_oi, ]
          to_autocorrelation_sp <- as(to_autocorrelation, "Spatial")
          st_geometry(to_autocorrelation) <- NULL # turn to_autocorrelation into data frame
          centroids <- coordinates(to_autocorrelation_sp)
          to_autocorrelation_points <- SpatialPointsDataFrame(coords = centroids, data = to_autocorrelation)
          nb<-knn2nb(knearneigh(to_autocorrelation_points)) 
          lw <- nb2listw(nb, zero.policy = TRUE)
          
          # calculate spatial autocorrelation
          moran_residual <- moran.mc(to_autocorrelation_points$residuals, lw, 500, zero.policy = TRUE)
          moran_onset <- moran.mc(to_autocorrelation_points$onset, lw, 500, zero.policy = TRUE)
          moran_plant <- moran.mc(to_autocorrelation_points$plant, lw, 500, zero.policy = TRUE)
          
          moran_i_residual <- moran_residual$statistic
          moran_i_pval_residual <- moran_residual$p.value
          moran_i_onset <- moran_onset$statistic
          moran_i_pval_onset <- moran_onset$p.value
          moran_i_plant <- moran_plant$statistic
          moran_i_pval_plant <- moran_plant$p.value
    
          
          # record whether predictors were present
          if ("lat" %in% predictors) {lat_predictor <- 'yes'} else {lat_predictor <- 'no'}
          if ("lon" %in% predictors) {lon_predictor <- 'yes'} else {lon_predictor <- 'no'}
          if ("year_index" %in% predictors) {year_predictor <- 'yes'} else {year_predictor <- 'no'}
          if ("region" %in% predictors) {region_predictor <- 'yes'} else {region_predictor <- 'no'}
          
          # save
          output_row <- data.frame(
            
            model_type = 'OLS',
            intensity = crop_intensity, plant_stat_type = plant_stat_type,
           
            lat_predictor = lat_predictor, lon_predictor = lon_predictor,
            year_predictor = year_predictor, region_predictor = region_predictor,
    
            onset_type = onset_type, precip_data = precip_data, onset_def_type = onset_def_type, 
            thres = thres, onset_scale = onset_scale,
            
            grid_size = grid_size, grid_offset_lat = lat_offset, grid_offset_lon = lon_offset,
            
            onset_coef = onset_coef, onset_coef_stderr = onset_coef_stderr,
            year_coef = year_coef, year_coef_stderr = year_coef_stderr,
            lat_coef = lat_coef, lat_coef_stderr = year_coef_stderr,
            
            
            R2 = R2, bias_meas = bias_measure, # slope of predicted plant to residual
            slope_onset_residual = onset_residual_slope, slope_fittedPlant_residual = fitted_residual_slope,
            
            moran_i_residual = moran_i_residual, moran_i_pval_residual = moran_i_pval_residual,
            moran_i_onset = moran_i_onset, moran_i_pval_onset = moran_i_pval_onset,
            moran_i_plant = moran_i_plant, moran_i_pval_plant = moran_i_pval_plant
          )
          
          output_results <- rbind(output_results, output_row)
          
          counter = counter + 1
          print(counter)
        }
      }
    }
  }
}

# export test results
filename = paste0('E:/R-code2/Modeling/output/robustness_test/', onset_type, '_OLS.RData')
save(output_results, file = filename)

```



## for the chosen onset type, loop through OLS model specifications with eliminated predictors

## export robustness test results for the given onset definition

```{r}

load("E:/R-code2/Modeling/output/robustness_test/Gabriel_onset_OLS.RData") 
```
