---
title: "Onset_Calculation_Point"
output: html_document
---

## repeat onset calculations in R and compare to GEE

# import and clean data

point 1: [-55.75269431542711,-12.791986265127166]
point 2: [-52.76441306542711,-12.577622747101971]
point 3: [-54.74195212792711,-15.645787864588819]

```{r}

library(ggplot2)

persiann_pt1 <- read.csv('E:/R-code2/Onset/data/persiann_pt1_precip.csv')
persiann_pt2 <- read.csv('E:/R-code2/Onset/data/persiann_pt2_precip.csv')
persiann_pt3 <- read.csv('E:/R-code2/Onset/data/persiann_pt3_precip.csv')
chirps_pt1 <- read.csv('E:/R-code2/Onset/data/chirps_pt1_precip.csv')
chirps_pt2 <- read.csv('E:/R-code2/Onset/data/chirps_pt2_precip.csv')
chirps_pt3 <- read.csv('E:/R-code2/Onset/data/chirps_pt3_precip.csv')

persiann <- data.frame(date = persiann_pt1$date,
                       precip_1 = persiann_pt1$precip,
                       precip_2 = persiann_pt2$precip,
                       precip_3 = persiann_pt3$precip) 

chirps <- data.frame(date = chirps_pt1$date,
                       precip_1 = chirps_pt1$precip,
                       precip_2 = chirps_pt2$precip,
                       precip_3 = chirps_pt3$precip) 

# add days after Aug 1
persiann$DOY_Aug1 <- seq(0, 363)
chirps$DOY_Aug1 <- seq(0, 363)

ggplot(persiann) +
  geom_line(aes(x = DOY_Aug1, y = precip_1), col = "black") +
  geom_line(aes(x = DOY_Aug1, y = precip_2), col = "blue") +
  geom_line(aes(x = DOY_Aug1, y = precip_3), col = "red") +
  ggtitle("PERSIANN") +
  ylim(c(0, 50)) +
  theme_bw()

ggplot(chirps) +
  geom_line(aes(x = DOY_Aug1, y = precip_1), col = "black") +
  geom_line(aes(x = DOY_Aug1, y = precip_2), col = "blue") +
  geom_line(aes(x = DOY_Aug1, y = precip_3), col = "red") +
  ggtitle("CHIRPS") +
  ylim(c(0, 50)) +
  theme_bw()
```

# Gabriel's 2014 onset
pt1: 60
pt2: 61
pt3: 60

## AA


## threshold
First day after Aug 1 with rainfall > threshold (10 mm)

```{r}

thres_onset <- function(precip_df, point, thres) {
  precip <- precip_df[,point]
  
  wet_days <- precip_df$DOY_Aug1[precip >= thres]
  
  if (length(wet_days) == 0) {onset <- 364}
  else {onset <- min(wet_days)}

  return(onset)
}

chosen_thres = 20

# print(thres_onset(precip_df = persiann, point = 'precip_1', thres = chosen_thres))
# print(thres_onset(precip_df = persiann, point = 'precip_2', thres = chosen_thres))
# print(thres_onset(precip_df = persiann, point = 'precip_3', thres = chosen_thres))
# 
# print(thres_onset(precip_df = chirps, point = 'precip_1', thres = chosen_thres))
# print(thres_onset(precip_df = chirps, point = 'precip_2', thres = chosen_thres))
print(thres_onset(precip_df = chirps, point = 'precip_3', thres = chosen_thres))

```


## rangethres

Earliest 10 days rainfall > x, subsequent 7 days rainfall > y
Onset happens at the END of the first range (before_range)

```{r}

precip <- persiann$precip_1

rangethres_onset <- function(precip_df, point, before_range, after_range, before_thres, after_thres) {
  precip <- precip_df[,point]
  
  # get all the possible before_starts
  total_range_dates <- before_range + after_range
  possible_before_starts = seq(1, 365 - total_range_dates, 1)
  
  # save sums in data frame
  precip_sums <- data.frame(
    before_start = numeric(length(possible_before_starts)),
    before_sum = numeric(length(possible_before_starts)),
    after_sum = numeric(length(possible_before_starts))
  )
  
  index = 1
  
  # calculate all possible sums
  for (before_start in possible_before_starts) {
    before_precips <- precip_df[precip_df$DOY_Aug1 >= before_start & 
                                 precip_df$DOY_Aug1 < before_start + before_range, point]
    before_sum <- sum(before_precips)
    
    after_precips <- precip_df[precip_df$DOY_Aug1 >= before_start + before_range & 
                                 precip_df$DOY_Aug1 < before_start + before_range + after_range, point]
    after_sum <- sum(after_precips)
    
    precip_sums[index, "before_start"] <- before_start
    precip_sums[index, "before_sum"] <- before_sum
    precip_sums[index, "after_sum"] <- after_sum
    
    index = index + 1
  }
  
  # filter sums for qualifying wet season days
  wet_days <- precip_sums[precip_sums$before_sum >= before_thres & precip_sums$after_sum >= after_thres, "before_start"]
  
  if (length(wet_days) == 0) {onset <- 364}
  else {onset <- min(wet_days) + before_range}

  return(onset)
}

chosen_before_thres = 7
chosen_after_thres = 3

print(rangethres_onset(precip_df = persiann, point = 'precip_1',
                       before_range = 10, after_range = 15,
                       before_thres = chosen_before_thres, after_thres = chosen_after_thres))
print(rangethres_onset(precip_df = persiann, point = 'precip_2',
                       before_range = 10, after_range = 15,
                       before_thres = chosen_before_thres, after_thres = chosen_after_thres))
print(rangethres_onset(precip_df = persiann, point = 'precip_3',
                       before_range = 10, after_range = 15,
                       before_thres = chosen_before_thres, after_thres = chosen_after_thres))

# print(rangethres_onset(precip_df = chirps, point = 'precip_1', 
#                        before_range = 10, after_range = 7, 
#                        before_thres = chosen_before_thres, after_thres = chosen_after_thres))
# print(rangethres_onset(precip_df = chirps, point = 'precip_2', 
#                        before_range = 10, after_range = 7, 
#                        before_thres = chosen_before_thres, after_thres = chosen_after_thres))
# print(rangethres_onset(precip_df = chirps, point = 'precip_3', 
#                        before_range = 10, after_range = 7, 
#                        before_thres = chosen_before_thres, after_thres = chosen_after_thres))
```

## pentad

Earliest pentad > x total rain, with earlier/later pentads of less/more rain

```{r}

pentad_onset <- function(precip_df, point, thres) {

  # get all the possible middle pentad starts
  # first possible middle pentad starts 5 days after start of year
  # last possible middle pentad starts 10 days before end of the year
  possible_midpent_starts <- seq(5, 354, 1) 
    
  # save sums in data frame
  precip_sums <- data.frame(
    middle_pentad_start = numeric(length(possible_midpent_starts)),
    first_pentad_sum = numeric(length(possible_midpent_starts)),
    middle_pentad_sum = numeric(length(possible_midpent_starts)),
    last_pentad_sum = numeric(length(possible_midpent_starts))
  )
    
  index = 1
    
    # calculate all possible sums
  for (midpent_start in possible_midpent_starts) {
      first_pentad_precips <- precip_df[precip_df$DOY_Aug1 >= midpent_start - 5 & 
                                   precip_df$DOY_Aug1 < midpent_start, point]
      first_pentad_sum <- sum(first_pentad_precips)
      
      middle_pentad_precips <- precip_df[precip_df$DOY_Aug1 >= midpent_start & 
                                   precip_df$DOY_Aug1 < midpent_start + 5, point]
      middle_pentad_sum <- sum(middle_pentad_precips)
      
      last_pentad_precips <- precip_df[precip_df$DOY_Aug1 >= midpent_start + 5 & 
                                   precip_df$DOY_Aug1 < midpent_start + 10, point]
      last_pentad_sum <- sum(last_pentad_precips)
      
      precip_sums[index, "middle_pentad_start"] <- midpent_start
      precip_sums[index, "first_pentad_sum"] <- first_pentad_sum
      precip_sums[index, "middle_pentad_sum"] <- middle_pentad_sum
      precip_sums[index, "last_pentad_sum"] <- last_pentad_sum
      
      index = index + 1
    }
    
  # filter sums for qualifying wet season days
  
  # first check for pentads > thres
  wet_days <- precip_sums[precip_sums$middle_pentad_sum >= thres & 
                            precip_sums$first_pentad_sum < precip_sums$middle_pentad_sum &
                            precip_sums$last_pentad_sum > precip_sums$middle_pentad_sum, "middle_pentad_start"]
    
  if (length(wet_days) == 0) {onset <- 364
  } else {onset <- min(wet_days)}
}

chosen_thres = 10
print(pentad_onset(precip_df = persiann, point = "precip_1", thres = chosen_thres))
print(pentad_onset(precip_df = persiann, point = "precip_2", thres = chosen_thres))
print(pentad_onset(precip_df = persiann, point = "precip_3", thres = chosen_thres))
# 
# print(pentad_onset(precip_df = chirps, point = "precip_1", thres = chosen_thres))
# print(pentad_onset(precip_df = chirps, point = "precip_2", thres = chosen_thres))
# print(pentad_onset(precip_df = chirps, point = "precip_3", thres = chosen_thres))

```

## Frequency

Onset starts when number of rainy days (rain > 1 mm) in 4 week period is more than x days
Onset is at the END of this 4 week period

```{r}
precip <- persiann$precip_1
precip_df <- persiann
point <- "precip_1"
num_days <- 3

freq_onset <- function(precip_df, point, num_days) {
  # get rainy days as boolean
  rainy_day <- precip_df[, point] >= 1
  
  possible_starts <- seq(1, 365 - 29)
  
  precip_counts = data.frame(
    start = numeric(length(possible_starts)),
    count = numeric(length(possible_starts))
  )
  
  index = 1
  for (start in possible_starts) {
    count <- sum(rainy_day[start:(start+28)])
    
    precip_counts[index, "start"] <- start
    precip_counts[index, "count"] <- count
    
    index = index + 1
  }
  
  wet_days <- precip_counts[precip_counts$count >= num_days, "start"]
  
  if (length(wet_days) == 0) {onset <- 364
  } else { onset <- min(wet_days) + 28 } # get the END of the four weeks as onset
  
  return(onset)
}

chosen_num_days = 10

print(freq_onset(precip_df = persiann, point = "precip_1", num_days = chosen_num_days))
print(freq_onset(precip_df = persiann, point = "precip_2", num_days = chosen_num_days))
print(freq_onset(precip_df = persiann, point = "precip_3", num_days = chosen_num_days))
# 
# print(freq_onset(precip_df = chirps, point = "precip_1", num_days = chosen_num_days))
# print(freq_onset(precip_df = chirps, point = "precip_2", num_days = chosen_num_days))
# print(freq_onset(precip_df = chirps, point = "precip_3", num_days = chosen_num_days))

```

## monsoon

Onset is the first wet day (> 1 mm, or wet_day_thres) that's followed by 10 days of rain >= 10 mm (or wet_days_thres)

```{r}

precip <- persiann$precip_1
precip_df <- persiann
point <- "precip_1"
wet_day_thres <- 1
wet_days_thres <- 10

monsoon_onset <- function(precip_df, point, wet_day_thres, wet_days_thres) {
  
  # get rainy days as boolean
  rainy_day <- precip_df[, point] >= wet_day_thres
  
  # the possible onsets are all the rainy_days that occur before DOY = 364 - wet_days_thres
  possible_starts <- precip_df[rainy_day, "DOY_Aug1"]
  possible_starts <- possible_starts[which(possible_starts < (364 - wet_days_thres))]
  
  precip_sums = data.frame(
      start = numeric(length(possible_starts)),
      sum = numeric(length(possible_starts))
    )
  
  index = 1
    for (start in possible_starts) {
      next_days_precip <- precip_df[start:(start+10), point]
      next_days_sum <- sum(next_days_precip)
      
      precip_sums[index, "start"] <- start
      precip_sums[index, "sum"] <- next_days_sum
      
      index = index + 1
    }
  
  
  wet_days <- precip_sums[precip_sums$sum >= wet_days_thres, "start"]
  
  if (length(wet_days) == 0) {onset <- 364
  } else { onset <- min(wet_days) }
  
  return(onset)
}

chosen_wet_day_thres = 1
chosen_wet_days_thres = 10

print(monsoon_onset(precip_df = persiann, point = "precip_1",
                    wet_day_thres = chosen_wet_day_thres, wet_days_thres = chosen_wet_days_thres))
print(monsoon_onset(precip_df = persiann, point = "precip_2",
                    wet_day_thres = chosen_wet_day_thres, wet_days_thres = chosen_wet_days_thres))
print(monsoon_onset(precip_df = persiann, point = "precip_3",
                    wet_day_thres = chosen_wet_day_thres, wet_days_thres = chosen_wet_days_thres))

print(monsoon_onset(precip_df = chirps, point = "precip_1",
                    wet_day_thres = chosen_wet_day_thres, wet_days_thres = chosen_wet_days_thres))
print(monsoon_onset(precip_df = chirps, point = "precip_2",
                    wet_day_thres = chosen_wet_day_thres, wet_days_thres = chosen_wet_days_thres))
print(monsoon_onset(precip_df = chirps, point = "precip_3", 
                    wet_day_thres = chosen_wet_day_thres, wet_days_thres = chosen_wet_days_thres))
```