---
title: "Bootstrapping"
output: html_document
---

## Read and summarize pixel level range errors from Planet validation data

```{r}

library(MASS)

p1_errors <- read.csv('p1_error_toBootstrap_v3.csv')
h1_errors <- read.csv('h1_error_toBootstrap_v3.csv')

p1_y <- p1_errors$p1_lowerBoundError - p1_errors$p1_upperBoundError
h1_y <- h1_errors$h1_lowerBoundError - h1_errors$h1_upperBoundError

# fit to normal distribution and plot
fit_p1_lowerBound <- fitdistr(p1_errors$p1_lowerBoundError, "normal")
para_p1_lowerBound <- fit_p1_lowerBound$estimate
hist(p1_errors$p1_lowerBoundError, prob = TRUE, main = "p1 lower bound error", xlab = 'error [days]')
curve(dnorm(x, para_p1_lowerBound[1], para_p1_lowerBound[2]), col = 2, add = TRUE)

fit_p1_upperBound <- fitdistr(p1_errors$p1_upperBoundError, "normal")
para_p1_upperBound <- fit_p1_upperBound$estimate
hist(p1_errors$p1_upperBoundError, prob = TRUE, main = "p1 upper bound error", xlab = 'error [days]')
curve(dnorm(x, para_p1_upperBound[1], para_p1_upperBound[2]), col = 2, add = TRUE)

fit_h1_lowerBound <- fitdistr(h1_errors$h1_lowerBoundError, "normal")
para_h1_lowerBound <- fit_h1_lowerBound$estimate
hist(h1_errors$h1_lowerBoundError, prob = TRUE, main = "h1 lower bound error", xlab = 'error [days]')
curve(dnorm(x, para_h1_lowerBound[1], para_h1_lowerBound[2]), col = 2, add = TRUE)

fit_h1_upperBound <- fitdistr(h1_errors$h1_upperBoundError, "normal")
para_h1_upperBound <- fit_h1_upperBound$estimate
hist(h1_errors$h1_upperBoundError, prob = TRUE, main = "h1 upper bound error", xlab = 'error [days]')
curve(dnorm(x, para_h1_upperBound[1], para_h1_upperBound[2]), col = 2, add = TRUE)

fit_h1_y <- fitdistr(h1_y, "normal")
para_h1_y <- fit_h1_y$estimate
hist(h1_y, prob = TRUE, main = "h1 y", xlab = 'error [days]')
curve(dnorm(x, para_h1_y[1], para_h1_y[2]), col = 2, add = TRUE)

fit_p1_y <- fitdistr(p1_y, "normal")
para_p1_y <- fit_p1_y$estimate
hist(p1_y, prob = TRUE, main = "p1 y", xlab = 'error [days]')
curve(dnorm(x, para_p1_y[1], para_p1_y[2]), col = 2, add = TRUE)

```

## Karina's way to calculate timing error distribution (with simulation)
## Results (mean, sd of pixel plant, harvest) will be called sim

```{r}
# let's generate realizations of alpha and beta values
niter <- 10000
a_p1_pred <- numeric(niter)
b_p1_pred <- numeric(niter)
a_h1_pred <- numeric(niter)
b_h1_pred <- numeric(niter)
error_p1_pred <- numeric(niter)
error_h1_pred <- numeric(niter)

for (i in 1:niter){ 
	a_p1_pred[i] <- rnorm(1, mean = para_p1_upperBound['mean'], sd = para_p1_upperBound['sd'])
	b_p1_pred[i] <- rnorm(1, mean = para_p1_lowerBound['mean'], sd = para_p1_lowerBound['sd'])
	a_h1_pred[i] <- rnorm(1, mean = para_h1_upperBound['mean'], sd = para_h1_upperBound['sd'])
	b_h1_pred[i] <- rnorm(1, mean = para_h1_lowerBound['mean'], sd = para_h1_lowerBound['sd'])
}

# let's generate realizations of epsilon values
for (i in 1:niter){ 
  error_p1_pred[i] <- runif(1, min = a_p1_pred[i], max = b_p1_pred[i])
  error_h1_pred[i] <- runif(1, min = a_h1_pred[i], max = b_h1_pred[i])
}

# get rid of NaN values (happens if a > b, in about 5% of cases)
error_p1_pred <- error_p1_pred[!is.na(error_p1_pred)]
error_h1_pred <- error_h1_pred[!is.na(error_h1_pred)]

# then you can evaluate the distribution of error_p1_pred, etc
#error_p1 <- density(error_p1_pred, kernel = c("gaussian"), na.rm = TRUE)

fit_error_p1_pred <- fitdistr(error_p1_pred, "normal")
para_error_p1_pred <- fit_error_p1_pred$estimate
hist(error_p1_pred, prob = TRUE, main = "p1 error, sim", xlab = 'error [days]')
curve(dnorm(x, para_error_p1_pred[1], para_error_p1_pred[2]), col = 2, add = TRUE)

fit_error_h1_pred <- fitdistr(error_h1_pred, "normal")
para_error_h1_pred <- fit_error_h1_pred$estimate
hist(error_h1_pred, prob = TRUE, main = "h1 error, sim", xlab = 'error [days]')
curve(dnorm(x, para_error_h1_pred[1], para_error_h1_pred[2]), col = 2, add = TRUE)

plant_error_mean_sim <- para_error_p1_pred[1]
plant_error_sd_sim <- para_error_p1_pred[2]
harvest_error_mean_sim <- para_error_h1_pred[1]
harvest_error_sd_sim <- para_error_h1_pred[2]

print(paste('plant pixel error', plant_error_mean_sim, '+/-', plant_error_sd_sim))
print(paste('harvest pixel error', harvest_error_mean_sim, '+/-', harvest_error_sd_sim))

```

## Numerically calculate timing error distribution
## Results (mean, sd of pixel plant, harvest) will be called fullCalc

```{r}
library(fBasics) # for Heaviside fcn
library(dplyr)

# vectors of a and y over which to integrate, and vector of x over which to calculate p(x)
as <- seq(-100, 100, 10)
bs <- seq(-100, 100, 10)
ys <- seq(0.1, 100, 10)
xs <- seq(-100, 100, 10)

# given value of a (upper bound), find p(a)
p_a <- function(a, plant_or_harv) {
  
  if (plant_or_harv == 'plant') {
    fitted_mean <- para_p1_upperBound[1]
    fitted_sd <- para_p1_upperBound[2]
  }
  
  else if (plant_or_harv == 'harvest') {
    fitted_mean <- para_h1_upperBound[1]
    fitted_sd <- para_h1_upperBound[2]
  }
  return(dnorm(a, mean = fitted_mean, sd = fitted_sd))
}

# given value of b (lower bound), find p(b)
p_b <- function(b, plant_or_harv) {
  
  if (plant_or_harv == 'plant') {
    fitted_mean <- para_p1_lowerBound[1]
    fitted_sd <- para_p1_lowerBound[2]
  }
  
  else if (plant_or_harv == 'harvest') {
    fitted_mean <- para_h1_lowerBound[1]
    fitted_sd <- para_h1_lowerBound[2]
  }
  return(dnorm(b, mean = fitted_mean, sd = fitted_sd))
}

# given value of y (b - a or lower bound - upper bound), find p(y)
p_y <- function(y, plant_or_harv) {
  
  if (plant_or_harv == 'plant') {
    fitted_mean <- para_p1_y[1]
    fitted_sd <- para_p1_y[2]
  }
  
  else if (plant_or_harv == 'harvest') {
    fitted_mean <- para_h1_y[1]
    fitted_sd <- para_h1_y[2]
  }
  return(dnorm(y, mean = fitted_mean, sd = fitted_sd))
}

# given value of x, return the value of the double integral
calc_integral <- function(x, plant_or_harv, as, ys) {
  
  # initialize matrix to hold the argument of the integrals
  num_as <- length(as)
  num_ys <- length(ys)
  result_matrix <- matrix(nrow = num_as, ncol = num_ys)
  
  for (a_index in 1:num_as) {
    for (y_index in 1:num_ys) {
      
      a <- as[a_index]
      y <- ys[y_index]
      
      prob_a <- p_a(a, plant_or_harv)
      prob_y <- p_y(y, plant_or_harv)
      
      H_a <- Heaviside(x, a = a)
      H_b <- Heaviside(x, a = (y + a))
      result <- prob_a*prob_y*(H_a - H_b)/y
      
      result_matrix[a_index, y_index] <- result
      
    }
  }
  
  return(sum(result_matrix))
}



# calculate p(x) - use either calc_integral or calc_integral_2
#prob_x_plant <- sapply(xs, calc_integral_2, plant_or_harv = 'plant', as = as, bs = bs)
#prob_x_harv <- sapply(xs, calc_integral_2, plant_or_harv = 'harvest', as = as, bs = bs)

prob_x_plant <- sapply(xs, calc_integral, plant_or_harv = 'plant', as = as, ys = ys)
prob_x_harv <- sapply(xs, calc_integral, plant_or_harv = 'harvest', as = as, ys = ys)


# fit p(x) to its own distribution (mean and sd) using nls()

plant_error_data <- data.frame(error=xs, density=prob_x_plant)
res <- nls( density ~ k*exp(-1/2*(error-mu)^2/sigma^2), start=c(mu=0,sigma=30,k=1) , data = plant_error_data,  control = nls.control(maxiter = 500))
plant_error_params <- summary(res)$parameters[,"Estimate"]
plant_error_mean_fullCalc <- plant_error_params[1]
plant_error_sd_fullCalc <- plant_error_params[2]
plant_error_scale_fullCalc <- plant_error_params[3]
plot(xs, prob_x_plant, main = 'p(error) for planting, fullCalc', xlab = 'error', ylab = 'density')
plot(function(x) plant_error_scale_fullCalc*exp(-1/2*(x-plant_error_mean_fullCalc)^2/plant_error_sd_fullCalc^2),col=2,add=T,xlim=range(plant_error_data$error))



harvest_error_data <- data.frame(error=xs, density=prob_x_harv)
res <- nls( density ~ k*exp(-1/2*(error-mu)^2/sigma^2), start=c(mu=0,sigma=30,k=1) , data = harvest_error_data,  control = nls.control(maxiter = 500))
harvest_error_params <- summary(res)$parameters[,"Estimate"]
harvest_error_mean_fullCalc <- harvest_error_params[1]
harvest_error_sd_fullCalc <- harvest_error_params[2]
harvest_error_scale_fullCalc <- harvest_error_params[3]
plot(xs, prob_x_harv, main = 'p(error) for harvest, fullCalc', xlab = 'error', ylab = 'density')
plot(function(x) harvest_error_scale_fullCalc*exp(-1/2*(x-harvest_error_mean_fullCalc)^2/harvest_error_sd_fullCalc^2),col=2,add=T,xlim=range(plant_error_data$error))

print(c('plant error mean', plant_error_mean_fullCalc))
print(c('plant error sd', plant_error_sd_fullCalc))

print(c('harvest error mean', harvest_error_mean_fullCalc))
print(c('harvest error sd', harvest_error_sd_fullCalc))

```
## Create land use cases

```{r}

# set up 50km x 50km cells, initialize with 10,000 'pixels'

prop_agri = 0.09 # proportion of the cell that is agriculture. in 2004, it was 0.07; in 2014, it was 0.11. calculated by GEE file LandCover/MapbiomasAgriCover

prop_SC = 15410/(15410 + 71581 + 3636) # proportion of training pts that are SC in 2007
prop_DC = 71581/(15410 + 71581 + 3636) # proportion of training pts that are DC in 2007
prop_nonsoy = 3636/(15410 + 71581 + 3636) # proportion of training pts that are nonsoy in 2007

total_pixels = 50000*50000/(500*500) # total number of 500m pixels in 50km cell

# calculate the number of each 
agri_pixels = total_pixels*prop_agri
SC_pixels = round(total_pixels*prop_agri*prop_SC)
DC_pixels = round(total_pixels*prop_agri*prop_DC)
nonsoy_pixels = round(total_pixels*prop_agri*prop_nonsoy)

# actual case (this is 'known' based on the ladn cover dataset)
actual_case = c(rep(0, SC_pixels), rep(1, DC_pixels), rep(2, nonsoy_pixels))

# generate a classified case

# start by calculating the indices of the falsely classified pixels, this can be used to index actual_case
wrong_SC <- sample(1:SC_pixels, 0.41*SC_pixels, replace=F)
wrong_DC <- sample((SC_pixels+1):(SC_pixels + DC_pixels), 0.14*DC_pixels, replace=F)
wrong_nonsoy <- sample((SC_pixels+DC_pixels+1):length(actual_case), 0.34*nonsoy_pixels, replace=F)

# calculate proportion of wrongly calculated pixels that are 'actually' which class
frac_wrong_SC_actual_DC = 301/(301+9)
frac_wrong_DC_actual_SC = 548/(548 + 128)
frac_wrong_nonsoy_actual_SC = 3/(3 + 53)

# of the falsely classified pixels, calculate the indices of the 'actual' classes
wrong_SC_actual_DC = sample(wrong_SC, frac_wrong_SC_actual_DC*length(wrong_SC), replace=F)
wrong_SC_actual_nonsoy = unique(wrong_SC[! wrong_SC %in%  wrong_SC_actual_DC])
wrong_DC_actual_SC = sample(wrong_DC, frac_wrong_DC_actual_SC*length(wrong_DC), replace = F)
wrong_DC_actual_nonsoy = unique(wrong_DC[! wrong_DC %in%  wrong_DC_actual_SC])
wrong_nonsoy_actual_SC = sample(wrong_nonsoy, frac_wrong_nonsoy_actual_SC*length(wrong_nonsoy), replace = F)
wrong_nonsoy_actual_DC = unique(wrong_nonsoy[! wrong_nonsoy %in%  wrong_nonsoy_actual_SC])

# for above, generate Two nested random choices: randomly choose the pixels whose land cover is 'falsely classified'; proportion is 100 - 59 % for SC (301/total wrongly predicted SC pts become DC; 9/total wrongly predicted SC pts become nonsoy agri); 100 - 86 % of DC must change (548/total wrongly predicted DC pts becomes SC, 128/total wrongly predicted DC pts becomes nonsoy agri); 100 - 66% of nonsoy agri must change (3/total wrongly predicted nonsoy pts becomes SC; 53/total wrongly predicted nonsoy pts becomes DC). total DC pts comes from confusion matrix.

# create one 'predicted/erroneous' set of pixels
classified_case <- actual_case # start with classified case = actual case, then replace the erroneous pixels


classified_case[wrong_SC_actual_DC] <- 1
classified_case[wrong_SC_actual_nonsoy] <- 2
classified_case[wrong_DC_actual_SC] <- 0
classified_case[wrong_DC_actual_nonsoy] <- 2
classified_case[wrong_nonsoy_actual_SC] <- 0
classified_case[wrong_nonsoy_actual_DC] <- 1


```

## Calculate errors due to land cover classification

```{r}


set.seed(124)

# given a land cover and plant/harvest, randomly generate planting and harvest pixel-level errors and take the median to simulate the error at 50km scale
calc_median_date <- function(agri_pixels, land_cover, plant_or_harv, plant_error_mean, plant_error_sd, harvest_error_mean, harvest_error_sd) {
  if (plant_or_harv == 'plant') {
    error_mean <- plant_error_mean
    error_sd <- plant_error_sd
  }
  
  else if (plant_or_harv == 'harvest') {
    error_mean <- harvest_error_mean
    error_sd <- harvest_error_sd
  }
  
  pixel_errors <- rnorm(agri_pixels, error_mean, error_sd)
  SC_median_error <- pixel_errors[land_cover == 0] %>% median
  DC_median_error <- pixel_errors[land_cover == 1] %>% median
  soy_median_error <- pixel_errors[land_cover <= 1] %>% median
  
  median_errors <- c(SC_median_error, DC_median_error, soy_median_error)
  names(median_errors) <- c('SC', 'DC', 'soy')
  
  return(median_errors)
}

# given the number of sims to do, calculate median timing for actual and classified land covers

calc_land_cover_error <- function(nsims, agri_pixels, actual_case, classified_case, plant_or_harv, plant_error_mean, plant_error_sd, harvest_error_mean, harvest_error_sd) {
  SC_diffs <- numeric(nsims)
  DC_diffs <- numeric(nsims)
  soy_diffs <- numeric(nsims)
  
  for (sim in 1:nsims) {
    actual_medians <- calc_median_date(agri_pixels, actual_case, plant_or_harv, plant_error_mean, plant_error_sd, harvest_error_mean, harvest_error_sd)
    classified_medians <- calc_median_date(agri_pixels, classified_case, plant_or_harv, plant_error_mean, plant_error_sd, harvest_error_mean, harvest_error_sd)
    
    SC_diffs[sim] <- actual_medians['SC'] - classified_medians['SC']
    DC_diffs[sim] <- actual_medians['DC'] - classified_medians['DC']
    soy_diffs[sim] <- actual_medians['soy'] - classified_medians['soy']
  }
  
  diffs <- data.frame(SC = SC_diffs, DC = DC_diffs, soy = soy_diffs)
  
  return(diffs)
}

# calculate difference in median dates between the two cases
harvest_lc_error_fullCalc <- calc_land_cover_error(500, agri_pixels, actual_case, classified_case, 'harvest', plant_error_mean_fullCalc, plant_error_sd_fullCalc, harvest_error_mean_fullCalc, harvest_error_sd_fullCalc)

plant_lc_error_fullCalc <- calc_land_cover_error(500, agri_pixels, actual_case, classified_case, 'plant', plant_error_mean_fullCalc, plant_error_sd_fullCalc, harvest_error_mean_fullCalc, harvest_error_sd_fullCalc)

harvest_lc_error_sim <- calc_land_cover_error(500, agri_pixels, actual_case, classified_case, 'harvest', plant_error_mean_sim, plant_error_sd_sim, harvest_error_mean_sim, harvest_error_sd_sim)

plant_lc_error_sim <- calc_land_cover_error(500, agri_pixels, actual_case, classified_case, 'plant', plant_error_mean_sim, plant_error_sd_sim, harvest_error_mean_sim, harvest_error_sd_sim)

hist(plant_lc_error_fullCalc$SC, main = 'SC plant lc error fullCalc')
hist(plant_lc_error_fullCalc$DC, main = 'DC plant lc error fullCalc')
hist(plant_lc_error_fullCalc$soy, main = 'soy plant lc error fullCalc')

hist(harvest_lc_error_fullCalc$SC, main = 'SC harvest lc error fullCalc')
hist(harvest_lc_error_fullCalc$DC, main = 'DC harvest lc error fullCalc')
hist(harvest_lc_error_fullCalc$soy, main = 'soy harvest lc error fullCalc')

hist(plant_lc_error_sim$SC, main = 'SC plant lc error sim')
hist(plant_lc_error_sim$DC, main = 'DC plant lc error sim')
hist(plant_lc_error_sim$soy, main = 'soy plant lc error sim')

hist(harvest_lc_error_sim$SC, main = 'SC harvest lc error sim')
hist(harvest_lc_error_sim$DC, main = 'DC harvest lc error sim')
hist(harvest_lc_error_sim$soy, main = 'soy harvest lc error sim')

# find mean and sd of land cover error
plant_lc_error_SC_mean_fullCalc <- max(mean(plant_lc_error_fullCalc$SC), 0)
plant_lc_error_DC_mean_fullCalc <- max(mean(plant_lc_error_fullCalc$DC), 0)
plant_lc_error_soy_mean_fullCalc <- max(mean(plant_lc_error_fullCalc$soy), 0)

plant_lc_error_SC_sd_fullCalc <- sd(plant_lc_error_fullCalc$SC)
plant_lc_error_DC_sd_fullCalc <- sd(plant_lc_error_fullCalc$DC)
plant_lc_error_soy_sd_fullCalc <- sd(plant_lc_error_fullCalc$soy)

harvest_lc_error_SC_mean_fullCalc <- max(mean(harvest_lc_error_fullCalc$SC), 0)
harvest_lc_error_DC_mean_fullCalc <- max(mean(harvest_lc_error_fullCalc$DC), 0)
harvest_lc_error_soy_mean_fullCalc <- max(mean(harvest_lc_error_fullCalc$soy), 0)

harvest_lc_error_SC_sd_fullCalc <- sd(harvest_lc_error_fullCalc$SC)
harvest_lc_error_DC_sd_fullCalc <- sd(harvest_lc_error_fullCalc$DC)
harvest_lc_error_soy_sd_fullCalc <- sd(harvest_lc_error_fullCalc$soy)

plant_lc_error_SC_mean_sim <- max(mean(plant_lc_error_sim$SC), 0)
plant_lc_error_DC_mean_sim <- max(mean(plant_lc_error_sim$DC), 0)
plant_lc_error_soy_mean_sim <- max(mean(plant_lc_error_sim$soy), 0)

plant_lc_error_SC_sd_sim <- sd(plant_lc_error_sim$SC)
plant_lc_error_DC_sd_sim <- sd(plant_lc_error_sim$DC)
plant_lc_error_soy_sd_sim <- sd(plant_lc_error_sim$soy)

harvest_lc_error_SC_mean_sim <- max(mean(harvest_lc_error_sim$SC), 0)
harvest_lc_error_DC_mean_sim <- max(mean(harvest_lc_error_sim$DC), 0)
harvest_lc_error_soy_mean_sim <- max(mean(harvest_lc_error_sim$soy), 0)

harvest_lc_error_SC_sd_sim <- sd(harvest_lc_error_sim$SC)
harvest_lc_error_DC_sd_sim <- sd(harvest_lc_error_sim$DC)
harvest_lc_error_soy_sd_sim <- sd(harvest_lc_error_sim$soy)
```

## Combine pixel estimate error and land cover error


```{r}

print_total_errors <- function(pixel_plant_mean, pixel_plant_sd, pixel_harvest_mean, pixel_harvest_sd,
                               lc_plant_SC_mean, lc_plant_DC_mean, lc_plant_soy_mean,
                               lc_plant_SC_sd, lc_plant_DC_sd, lc_plant_soy_sd,
                               lc_harvest_SC_mean, lc_harvest_DC_mean, lc_harvest_soy_mean,
                               lc_harvest_SC_sd, lc_harvest_DC_sd, lc_harvest_soy_sd,
                               typeOfCalc) {
  
  total_plant_SC_error_mean <- pixel_plant_mean + lc_plant_SC_mean
  total_plant_DC_error_mean <- pixel_plant_mean + lc_plant_DC_mean
  total_plant_soy_error_mean <- pixel_plant_mean + lc_plant_soy_mean
  
  total_plant_SC_error_sd <- pixel_plant_sd + lc_plant_SC_sd
  total_plant_DC_error_sd <- pixel_plant_sd + lc_plant_DC_sd
  total_plant_soy_error_sd <- pixel_plant_sd + lc_plant_soy_sd
  
  total_harvest_SC_error_mean <- pixel_harvest_mean + lc_harvest_SC_mean
  total_harvest_DC_error_mean <- pixel_harvest_mean + lc_harvest_DC_mean
  total_harvest_soy_error_mean <- pixel_harvest_mean + lc_harvest_soy_mean
  
  total_harvest_SC_error_sd <- pixel_harvest_sd + lc_harvest_SC_sd
  total_harvest_DC_error_sd <- pixel_harvest_sd + lc_harvest_DC_sd
  total_harvest_soy_error_sd <- pixel_harvest_sd + lc_harvest_soy_sd
  
  # print out the errors
  print(typeOfCalc)
  print(paste(typeOfCalc, 'plant SC error:', total_plant_SC_error_mean, '+/-', total_plant_SC_error_sd, 'days'))
  print(paste(typeOfCalc, 'harvest SC error:', total_harvest_SC_error_mean, '+/-', total_harvest_SC_error_sd, 'days'))
  
  print(paste(typeOfCalc, 'plant DC error:', total_plant_DC_error_mean, '+/-', total_plant_DC_error_sd, 'days'))
  print(paste(typeOfCalc, 'harvest DC error:', total_harvest_DC_error_mean, '+/-', total_harvest_DC_error_sd, 'days'))
  
  print(paste(typeOfCalc, 'plant soy error:', total_plant_soy_error_mean, '+/-', total_plant_soy_error_sd, 'days'))
  print(paste(typeOfCalc, 'harvest soy error:', total_harvest_soy_error_mean, '+/-', total_harvest_soy_error_sd, 'days'))
}

print_total_errors(plant_error_mean_fullCalc, plant_error_sd_fullCalc, harvest_error_mean_fullCalc, harvest_error_sd_fullCalc,
                   plant_lc_error_SC_mean_fullCalc, plant_lc_error_DC_mean_fullCalc, plant_lc_error_soy_mean_fullCalc,
                   plant_lc_error_SC_sd_fullCalc, plant_lc_error_DC_sd_fullCalc, plant_lc_error_soy_sd_fullCalc,
                   harvest_lc_error_SC_mean_fullCalc, harvest_lc_error_DC_mean_fullCalc, harvest_lc_error_soy_mean_fullCalc,
                   harvest_lc_error_SC_sd_fullCalc, harvest_lc_error_DC_sd_fullCalc, harvest_lc_error_soy_sd_fullCalc,
                   "fullCalc")

print_total_errors(plant_error_mean_sim, plant_error_sd_sim, harvest_error_mean_sim, harvest_error_sd_sim,
                   plant_lc_error_SC_mean_sim, plant_lc_error_DC_mean_sim, plant_lc_error_soy_mean_sim,
                   plant_lc_error_SC_sd_sim, plant_lc_error_DC_sd_sim, plant_lc_error_soy_sd_sim,
                   harvest_lc_error_SC_mean_sim, harvest_lc_error_DC_mean_sim, harvest_lc_error_soy_mean_sim,
                   harvest_lc_error_SC_sd_sim, harvest_lc_error_DC_sd_sim, harvest_lc_error_soy_sd_sim,
                   "sim")
```

## unused

```{r}
# given value of x, return the value of the double integral. DOESN'T GIVE A RESULT THAT'S FITTABLE WITH NLS()
calc_integral_2 <- function(x, plant_or_harv, as, bs) {
  
  # initialize matrix to hold the argument of the integrals
  num_as <- length(as)
  num_bs <- length(bs)
  result_matrix <- matrix(nrow = num_as, ncol = num_bs)
  
  for (a_index in 1:num_as) {
    for (b_index in 1:num_bs) {
      
      a <- as[a_index]
      b <- bs[b_index]
      
      prob_a <- p_a(a, plant_or_harv)
      prob_b <- p_b(b, plant_or_harv)
      
      H_a <- Heaviside(x, a = a)
      H_b <- Heaviside(x, a = b)
      result <- prob_a*prob_b*(H_a - H_b)/(b - a)
      
      result_matrix[a_index, b_index] <- result
      
    }
  }
  
  return(sum(result_matrix))
}
```
