---
title: "Onset_Selection"
output: html_document
---


```{r}

# import data

```

Perform chosen FE model specification for each onset definition

```{r}

# do FE model, tabulate onset coef for different intensities, precip datasets, percentiles

```

Plot onset coefficient for each onset x precip x scale

```{r}

# include error bars for sampling grid location
# FE model for each intensity and percentile
# group the x axis by precip type, scale

# barplots for the most frequently occuring 'top onset' across intensities and percentiles

```

Plot of within-year spatial variability for each onset definition

```{r}

# boxplot or barplot, year on x axis

```

Map of within-year spatial variability (averaged quantiles through the years) for onsets and planting

```{r}



```

Map of long-term spatial pattern in differences between onset definitions

```{r}

# subtract AA definition from the top onset definitions

# subtract the top onset definitions from each other

# subtract, within a single onset definition, the result of using different thresholds

```

Timeseries of onset, averaged over space

```{r}

# error bars for spatial variability?

```

Robustness tests

```{r}

# eliminated predictors: repeat the OLS and FE specifications with eliminated predictors for the chosen onset definition. report onset coefficient for each intensity, percentile

# summarize uncertainty in onset coef as a standard deviation

# two-group t-test comparing onset coefficients for different onset definitions, cropping intensities, and percentiles
# calc onset coef difference t-test between SC and DC for each onset def, percentile
# calc onset coef difference t-test between onset definitions, for each percentile and intenssity
# calc onset coef difference t-test between percentiles, for each onset definition

```

Plot of onset coefficient sensitivity to eliminated predictors

```{r}

# different degrees of elimianted predictors on x axis, and onset coef on y axis

```

Plot of onset coefficients for different onset definitions, intensities, and percentiles

```{r}

```


